Higher-Order unification for free!

### 2024-07-01 paper/main.tex
line 247: Using "subscript" as a verb is odd. Revise that sentence.

\noindent
When it is clear from the context, we shall use the same syntax for \Fo{} terms
(although we never subscripts unification variables).\\
We use $s$, $s_1$, \ldots for terms in \Fo{} and $t$, $t_1$, \ldots for
terms in \Ho{}.

>>>>

\noindent
When it is clear from the context, we shall use the same syntax for \Fo{} terms
(although we never use subscripts for unification variables).\\
We use $s$, $s_1$, \ldots for terms in \Fo{} and $t$, $t_1$, \ldots for
terms in \Ho{}.
